X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2013-12-16 hedpc.tex
marcos letter

\section*{Competing financial interests}
The authors declare no competing financial interests.

@@

\end{thebibliography}
\section*{Author contributions}
TT and AM wrote the manuscript text and performed the experiments. All
authors reviewed the manuscript.
\end{document}

>>>>

\section*{Additional information}
The authors declare no competing financial interests.

@@

\end{thebibliography}

\section*{Author contributions}
T.T. and M.A. wrote the manuscript text and performed the experiments. All
authors reviewed the manuscript.
\end{document}
